Recovery of mountain plant communities in response to reductions in Nitrogen emissions is hidden by other drivers of global change

### 2018-06-14 Manuscript.Rmd
Grafik zur Verteilung der NDep über die Plots (Zustand und Veränderung).

## Potential effects of reduction in Nitrogen emmissions {-}
```{r cl, fig.cap="Colonization (a) and local survival (b) of oligotrophic (Ellenberg N = 2; red line) and eutrophic (Ellengerg N = 4) species along the N deposition gradient. Given are means and 95\\%-Credible Intervals from logistic linear mixed models. The vertical lines indicat the deposition rate with equal colonization or survival probabilities for oligotrophic and eutrophic species with the solid line indicating the median and the dashed lines the 5\\% and 95\\% quantiels of the margional posterior distribution."}
X <- 1:30
Xsd <- (X - 10) / 10

@@

# Colonization
load("Modelfit/colonization-N.RData")
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
CLs <- map_dbl(post, "CL")
CL_col <- median(CLs, na.rm = TRUE)
p1 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
  labs(title = "(a) Colonization", 
       y = "Colonization probability", 
       x = expression(paste("Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")"))) +
  geom_vline(xintercept = median(CLs, na.rm = TRUE)) +
  geom_vline(xintercept = quantile(CLs, probs = 0.05, na.rm = TRUE), lty = 2) +
  geom_vline(xintercept = quantile(CLs, probs = 0.95, na.rm = TRUE), lty = 2) +
  xlim(0,30)

# Local survival
load("Modelfit/localsurvival-N.RData")
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
CLs <- map_dbl(post, "CL") 
CL_surv <- median(CLs, na.rm = TRUE)
p2 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
  labs(title = "(b) Local survival", 
       y = "Local survival probability", 
       x = expression(paste("Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")"))) +
  geom_vline(xintercept = mean(CLs, na.rm = TRUE)) +
  geom_vline(xintercept = quantile(CLs, probs = 0.05, na.rm = TRUE), lty = 2) +
  geom_vline(xintercept = quantile(CLs, probs = 0.95, na.rm = TRUE), lty = 2) +
  xlim(0,30)

>>>>

## Potential effects of reduction in Nitrogen emmissions {-}
```{r Ndepchange, fig.cap="(a) The nitrogen deposition in 2010 and (b) the change in Nitrogen deposition between 2000 and 2010 along the elevational gradient of the study sites."}
p1 <- ggplot(sites, aes(x = Elevation * 500 + 1000, y = NTOT_2000)) +
  geom_point(cex = 0.8) +
  geom_smooth(method = loess) +
  geom_abline(intercept = 0, slope = 0, lty = 3) +
  labs(title = "(a) Nitrogen deposition in 2010", 
       y = expression(paste("Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")")), 
       x = "Elevation (m)") 
p2 <- ggplot(sites, aes(x = Elevation * 500 + 1000, y = (NTOT_2010 - NTOT_2000) )) +
  geom_point(cex = 0.8) +
  geom_smooth(method = loess)  +
  labs(title = "(b) Temporal change (2000 to 2010)", 
       y = expression(paste(Delta, "Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")")), 
       x = "Elevation (m)") +
  geom_hline(yintercept = 0, lty = 2) 
multiplot(p1, p2, cols = 2)
```

Nitrogen deposition decreased with increasing elevation (\@ref(fig:Ndepchange)a). In 2010 only `r 100 * mean(sites$NTOT_2010 < 10)`% of sites had a Nitrogen deposition rate of less than 10 kg N ha$^{-1}$ yr$^{-1}$, which lied all above 1000m. Between 2000 and 2010 the Nitrogen deposition decreased in average around 2 kg N ha$^{-1}$ yr$^{-1}$ with slightly larger net decreases at lower elevation (\@ref(fig:Ndepchange)a).

```{r cl, fig.cap="Colonization (a) and local survival (b) of oligotrophic (Ellenberg N = 2; red line) and eutrophic (Ellengerg N = 4) species along the N deposition gradient. Given are means and 95\\%-Credible Intervals from logistic linear mixed models. The vertical lines indicat the deposition rate with equal colonization or survival probabilities for oligotrophic and eutrophic species with the solid line indicating the median and the dashed lines the 5\\% and 95\\% quantiels of the margional posterior distribution."}
X <- 1:30
Xsd <- (X - 10) / 10

@@

# Colonization
load("Modelfit/colonization-N.RData")
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
CLs <- map_dbl(post, "CL")
CL_col <- median(CLs, na.rm = TRUE)
p1 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
  labs(title = "(a) Colonization", 
       y = "Colonization probability", 
       x = expression(paste("Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")"))) +
  geom_vline(xintercept = median(CLs, na.rm = TRUE)) +
  geom_vline(xintercept = quantile(CLs, probs = 0.05, na.rm = TRUE), lty = 2) +
  geom_vline(xintercept = quantile(CLs, probs = 0.95, na.rm = TRUE), lty = 2) +
  xlim(0,30) + theme(legend.position = c(0.75, 0.9)) + 
  scale_color_manual(labels = c("Nutrients value = 2", "Nutrients value = 4"), 
                     values = tcol[c(2,4)])

# Local survival
load("Modelfit/localsurvival-N.RData")
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
CLs <- map_dbl(post, "CL") 
CL_surv <- median(CLs, na.rm = TRUE)
p2 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
  labs(title = "(b) Local survival", 
       y = "Local survival probability", 
       x = expression(paste("Nitrogen deposition (kg ", ha^{-1}," ", yr^{-1}, ")"))) +
  geom_vline(xintercept = mean(CLs, na.rm = TRUE)) +
  geom_vline(xintercept = quantile(CLs, probs = 0.05, na.rm = TRUE), lty = 2) +
  geom_vline(xintercept = quantile(CLs, probs = 0.95, na.rm = TRUE), lty = 2) +
  xlim(0,30) + theme(legend.position = c(0.75, 0.9)) + 
  scale_color_manual(labels = c("Nutrients value = 2", "Nutrients value = 4"), 
                     values = tcol[c(2,4)])
